### 2015-05-14 Draft/evaluation.tex
Made best values bold in Table 2
Closes #6
Incorporated Feedback by Maria

\begin{itemize}
	\item\textbf{RQ1}: What are the precision and recall of \tool\ in identifying temporal constraints from sentences written in natural language?
	Answer to this question quantifies the effectiveness of \tool\ in identifying constraint sentences.
	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from constraint sentences in the API documents?
	Answer to this question quantifies the effectiveness of \tool\ in inferring temporal constraints from constraint sentences. 
	\item\textbf{RQ3}: What is the degree of the overlap between the temporal constraints inferred from natural language text in comparison to the typed-enforced temporal constraints?

@@

\begin{table*}
\begin{center}
\vspace*{-3ex}
\caption{Evaluation Results (Identification)}
\vspace*{-1ex}
\begin{tabular}{rlccccccccc}
\topline
\headcol S. No. & Trainer	& P$_{wrd}$	& R$_{wrd}$	& F$_{wrd}$	& P$_{ftr}$	& R$_{ftr}$	& F$_{ftr}$	& P$_{\Delta}$	& R$_{\Delta}$	& F$_{\Delta}$	\\
\midline 
			1	& AdaBoost			& 0.52	& 0.81	& 0.61	& 0.7	& 0.78	& 0.74	& 0.18	& -0.03	& 0.13	\\
\rowcol		2	& NaiveBayes		& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
			3	& Balanced Winnow	& 0.77	& 0.76	& 0.76	& 0.78	& 0.77	& 0.77	& 0.01	& 0.01	& 0.01	\\
\rowcol		4	& Decision Tree		& 0.82	& 0.58	& 0.66	& 0.92	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
			5	& Winnow			& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& 0.61	& 0.1	& 0.44	\\
\rowcol		6	& MaxEnt			& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
			7	& c45				& 0.78	& 0.4	& 0.52	& 0.82	& 0.59	& 0.67	& 0.04	& 0.19	& 0.15	\\
\midline
			& Average			& 0.61	& 0.59	& 0.54	& 0.79	& 0.6	& 0.65	& 0.18	& 0.01	& 0.11	\\
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{5in}}{\small
All values are average over 10-fold cross validation;
P: Precision; R: Recall; F: F-Score;
$_{wrd}$: No features used for training;
$_{ftr}$: features used for training;
$_{\Delta}$: improvement factor ($_{ftr}$ - $_{wrd}$)} \\ 
\end{tabular}
\label{tab:resultsRQ1}
\vspace*{-5ex}
\end{center}
\end{table*}

@@

To address this question, we manually inspected each of the constraints reported by ICON and classify it as a type-enforced constraint or a non type-enforced constraint. 
We observed that none of the constraints inferred by our \tool\ from natural language text were classified as a type-enforced constraint.
Hence, the constraints detected by \tool\ are not trivial enough to be enforced by a type system.

>>>>

\begin{itemize}
	\item\textbf{RQ1}: What are the precision and recall of \tool\ in identifying natural language sentences describing temporal constraints?
	Answer to this question quantifies the effectiveness of \tool\ in identifying constraint sentences.
	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from constraint sentences in the API documents?
	Answer to this question quantifies the effectiveness of \tool\ in inferring temporal constraints from constraint sentences. 
	\item\textbf{RQ3}: What is the degree of the overlap between the temporal constraints inferred from natural language text in comparison to the typed-enforced temporal constraints?

@@

\begin{table*}
\begin{center}
\vspace*{-3ex}
\caption{Evaluation Results (Identification)}
\vspace*{-1ex}
\begin{tabular}{rlccccccccc}
\topline
\headcol S. No. & Trainer	& P$_{wrd}$	& R$_{wrd}$	& F$_{wrd}$	& P$_{ftr}$	& R$_{ftr}$	& F$_{ftr}$	& P$_{\Delta}$	& R$_{\Delta}$	& F$_{\Delta}$	\\
\midline 
			1	& AdaBoost			& 0.52	& \textbf{0.81}	& 0.61	& 0.7	& \textbf{0.78}	& 0.74	& 0.18	& -0.03	& 0.13	\\
\rowcol		2	& NaiveBayes		& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
			3	& Balanced Winnow	& 0.77	& 0.76	& \textbf{0.76}	& 0.78	& 0.77	& \textbf{0.77}	& 0.01	& 0.01	& \textbf{0.01}	\\
\rowcol		4	& Decision Tree		& \textbf{0.82}	& 0.58	& 0.66	& \textbf{0.92}	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
			5	& Winnow			& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& \textbf{0.61}	& 0.1	& \textbf{0.44}	\\
\rowcol		6	& MaxEnt			& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
			7	& c45				& 0.78	& 0.4	& 0.52	& 0.82	& 0.59	& 0.67	& 0.04	& 0.19	& 0.15	\\
\midline
			& Average			& 0.61	& 0.59	& 0.54	& 0.79	& 0.6	& 0.65	& 0.18	& 0.01	& 0.11	\\
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{5in}}{\small
All values are average over 10-fold cross validation;
P: Precision; R: Recall; F: F-Score;
$_{wrd}$: No features used for training;
$_{ftr}$: features used for training;
$_{\Delta}$: improvement factor ($_{ftr}$ - $_{wrd}$)} \\ 
\end{tabular}
\label{tab:resultsRQ1}
\vspace*{-5ex}
\end{center}
\end{table*}

@@

To address this question, we manually inspected each of the constraints reported by ICON and classify it as a type-enforced constraint or a non type-enforced constraint. 
We observed that none of the constraints inferred by \tool\ from natural language text were classified as a type-enforced constraint.
Hence, the constraints detected by \tool\ are not trivial enough to be enforced by a type system.
